---
title: "10ksim_runs"
author: "Greg Knowlton"
date: "3/14/2021"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.width = 12,
  fig.height = 8,
  fig.align = "center"
)
library(kableExtra)
library(dplyr)
library(dampack)
library(tidyr)
df <- readRDS("data/basecase_output_cleaned.rds")
```

prepCov is PrEP coverage (prevalent/eligible population)
init cov is the coverage of the initiation app (prevalent app users/eligible population)

```{r}
coverage <- df %>%
    mutate(Strategy = as.factor(paste0(ifelse(prep.optim.init == T, "I", "-"),
                                       ifelse(prep.optim.adhr == T, "A", "-"),
                                       ifelse(prep.optim.retn == T, "P", "-")))) %>%
    select(-c(prep.optim.init, prep.optim.adhr, prep.optim.retn)) %>%
  select(Strategy, prep.optim.init.prob, prep.optim.adhr.prob, prep.optim.retn.prob, 
         prepElig_mean, prepCurr_mean, OptimInitUserPrev_mean, OptimInitUserPop_mean) %>%
  mutate(prepCov = prepCurr_mean/prepElig_mean,
         initCov = OptimInitUserPrev_mean / OptimInitUserPop_mean) %>%
  select(-c(prepElig_mean, prepCurr_mean, OptimInitUserPrev_mean, OptimInitUserPop_mean))

coverage %>%
  kable() %>%
  kable_styling()
```

```{r}
df[1, ] <- df[16, ]
df[17, ] <- df[16, ]
```

BASE CASE COVERAGE
30% start adherence intervention
40% start retention intervention
22.5% of undiagnosed MSM are using initiation app

```{r}
fixed <- sum((1 - 0.03) ^ (1:(52*10) / 52) * (1659.54*12 / 52))
init.adj <- 172.33 / 93.28

df_cov <- df[9:16,]
  df_strat <- df_cov %>%
    mutate(Strategy = as.factor(paste0(ifelse(prep.optim.init == T, "I", "-"),
                                       ifelse(prep.optim.adhr == T, "A", "-"),
                                       ifelse(prep.optim.retn == T, "P", "-")))) %>%
    select(-c(prep.optim.init, prep.optim.adhr, prep.optim.retn)) %>%
    rowwise() %>%
    mutate(cuml.init.int.cost.disc_std = ifelse(cuml.init.int.cost.disc_mean == 0,
                                                0,
                                                (cuml.init.int.cost.disc_mean - fixed) * init.adj + fixed),
           cuml.cost.disc_mean = cuml.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std,
           int.cost.disc_mean = int.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std)

  plotdat <- df_strat %>% select(Strategy, incid_mean, int.cost.disc_mean,
                                 cuml.cost.disc_mean, cuml.qaly.disc_mean)

  icer_df <- data.frame(Strategy = unique(df_strat$Strategy))
  icer_df$cost <- 10*df_strat$cuml.cost.disc_mean
  icer_df$qaly <- 10*df_strat$cuml.qaly.disc_mean

  icers <- calculate_icers(cost = icer_df$cost,
                           effect = icer_df$qaly,
                           strategies = icer_df$Strategy)
  # icers
  plot(icers, label = "all")

  extra_outcomes <- plotdat %>%
    group_by(Strategy) %>%
    summarize(intervention_cost = 10*mean(int.cost.disc_mean),
              cuml_incidence = 10*mean(incid_mean),
              .groups = "keep") %>%
    ungroup() %>%
    mutate(infections_averted = (first(cuml_incidence) - cuml_incidence),
           pct_infections_averted = 100*(infections_averted / (first(cuml_incidence))))

  icers_exp <- left_join(icers, extra_outcomes, by = "Strategy")

  sq <- icers_exp %>% filter(Strategy == "---")

  icers_exp <- icers_exp %>%
    mutate(pct_intervention_cost = 100 * (intervention_cost / Cost),
           Cost_sq_diff = Cost - sq$Cost,
           Effect_sq_diff = Effect - sq$Effect)
  icers_exp %>% 
  select(-c("cuml_incidence", "pct_intervention_cost")) %>%
  kable() %>%
  kable_styling()

```


```{r}
im.outcomes <- df_strat %>% select(Strategy,
                                   prep.cost.disc_mean,  cuml.cost.disc_mean,
                                   cuml.qaly.disc_mean,
                                   cuml.init.int.cost.disc_std, cuml.adhr.int.cost.disc_mean,
                                   cuml.retn.int.cost.disc_mean, hiv.test.cost.disc_mean, tot.visit.cost.disc_mean,
                                   int.cost.disc_mean, cc.cost.disc_mean) %>%
  group_by(Strategy) %>%
  summarize(across(everything(), mean, na.rm = TRUE))

cost.long <- im.outcomes %>% select(Strategy, hiv.test.cost.disc_mean,
                                   tot.visit.cost.disc_mean,
                                   int.cost.disc_mean,
                                   cc.cost.disc_mean,
                                   prep.cost.disc_mean) %>%
  group_by(Strategy) %>%
  pivot_longer(cols = 2:6) %>%
  mutate(name = factor(name,
                       levels = c("hiv.test.cost.disc_mean",
                                  "tot.visit.cost.disc_mean",
                                  "int.cost.disc_mean",
                                  "cc.cost.disc_mean",
                                  "prep.cost.disc_mean"),
                       labels = c("HIV Testing",
                                  "PrEP Visits",
                                  "Intervention Costs",
                                  "Other Clinical Care/Health Care Costs",
                                  "PrEP Drug Costs")))

sq.cost <- cost.long %>%
  filter(Strategy == "---") %>%
  mutate(sq_val = value) %>%
  ungroup() %>%
  select(-c(value, Strategy))

diff.cost <- cost.long %>%
  filter(Strategy != "---") %>%
  left_join(sq.cost, by = "name") %>%
  rowwise() %>%
  mutate(diff = value - sq_val,
         diff.prop = (value - sq_val)/sq_val)

cost.long.prop <- im.outcomes %>% select(Strategy, hiv.test.cost.disc_mean,
                                         tot.visit.cost.disc_mean,
                                         int.cost.disc_mean,
                                         cc.cost.disc_mean,
                                         prep.cost.disc_mean) %>%
  rowwise() %>%
  mutate(total = sum(c(hiv.test.cost.disc_mean, tot.visit.cost.disc_mean, int.cost.disc_mean, cc.cost.disc_mean, prep.cost.disc_mean)),
         hiv.test.cost.disc_mean = 100* hiv.test.cost.disc_mean / total,
         tot.visit.cost.disc_mean = 100 * tot.visit.cost.disc_mean / total,
         int.cost.disc_mean = 100 * int.cost.disc_mean / total,
         cc.cost.disc_mean = 100 * cc.cost.disc_mean / total,
         prep.cost.disc_mean = 100 * prep.cost.disc_mean / total) %>%
  select(-total) %>%
  group_by(Strategy) %>%
  pivot_longer(cols = 2:6) %>%
  mutate(Cost_source = factor(name,
                       levels = c("hiv.test.cost.disc_mean",
                                  "tot.visit.cost.disc_mean",
                                  "int.cost.disc_mean",
                                  "cc.cost.disc_mean",
                                  "prep.cost.disc_mean"),
                       labels = c("HIV Testing",
                                  "PrEP Visits",
                                  "Intervention Costs",
                                  "Other Clinical Care/Health Care Costs",
                                  "PrEP Drug Costs")),
         Proportion_of_total_cost = value) %>% select(-c("name", "value"))
cost.long.prop %>% kable() %>% kable_styling()

```

```{r, fig.width = 10, fig.height = 1, fig.align = "center"}
prep.costs <- seq(from = 3000, to = 25188, length.out = 200)
opt_strat <- rep(NA, 200)
for (i in 1:length(prep.costs)) {
  df_strat <- df_cov %>%
    mutate(Strategy = as.factor(paste0(ifelse(prep.optim.init == T, "I", "-"),
                                       ifelse(prep.optim.adhr == T, "A", "-"),
                                       ifelse(prep.optim.retn == T, "P", "-")))) %>%
    select(-c(prep.optim.init, prep.optim.adhr, prep.optim.retn)) %>%
  rowwise() %>%
    mutate(cuml.init.int.cost.disc_std = ifelse(cuml.init.int.cost.disc_mean == 0,
                                                0,
                                                (cuml.init.int.cost.disc_mean - fixed) * init.adj + fixed),
           cuml.cost.disc_mean = cuml.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std - 
             prep.cost.disc_mean + (prep.cost.disc_mean * (prep.costs[i]/16575.96)),
           int.cost.disc_mean = int.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std,
           nmb = 100000*cuml.qaly.disc_mean - cuml.cost.disc_mean) %>%
    group_by(Strategy) %>%
    summarize(nmb_mean = mean(nmb, na.rm = TRUE), .groups = "keep")

  opt_strat[i] <- as.character(df_strat$Strategy[which.max(df_strat$nmb_mean)])
}

opt_df <- data.frame(prep_cost = prep.costs, opt_strat = factor(opt_strat, levels = rev(levels(df_strat$Strategy))))

min <- opt_df %>% group_by(opt_strat) %>% filter(prep_cost == min(prep_cost)) %>% mutate(smin = prep_cost) %>% select(-prep_cost)
max <- opt_df %>% group_by(opt_strat) %>% filter(prep_cost == max(prep_cost)) %>% mutate(smax = prep_cost) %>% select(-prep_cost)
opt_plot <- left_join(min, max)
g <- ggplot(opt_plot) +
    geom_rect(data = opt_plot, aes(xmin = smin/12, xmax = smax/12,
                   ymin = 0, ymax = 1,
                   fill = opt_strat),
              position = "identity") + xlab("Monthly PrEP cost ($)") +
    theme(axis.line.y = element_blank(),
          axis.text.y = element_blank(),
          axis.title.y = element_blank(),
          axis.ticks.y = element_blank()) +
  labs(fill = "Optimal Strategy")
g
```


```{r, fig.width = 10, fig.height = 4, fig.align = "center"}
int.cost <- seq(from = 0, to = 5, length.out = 200)
opt_strat_all <- rep(NA, 200)
opt_strat_init <- rep(NA, 200)
opt_strat_adhr <- rep(NA, 200)
opt_strat_retn <- rep(NA, 200)
for (i in 1:length(int.cost)) {
  df_strat <- df_cov %>%
    mutate(Strategy = as.factor(paste0(ifelse(prep.optim.init == T, "I", "-"),
                                       ifelse(prep.optim.adhr == T, "A", "-"),
                                       ifelse(prep.optim.retn == T, "P", "-")))) %>%
    select(-c(prep.optim.init, prep.optim.adhr, prep.optim.retn)) %>%
  rowwise() %>%
    mutate(cuml.init.int.cost.disc_std = ifelse(cuml.init.int.cost.disc_mean == 0,
                                                0,
                                                (cuml.init.int.cost.disc_mean - fixed) * init.adj + fixed),
           int.cost.disc_mean = int.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std,
           cuml.cost.disc_mean = cuml.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std,
           cuml.cost.disc_std = cuml.cost.disc_mean - int.cost.disc_mean + int.cost[i]*int.cost.disc_mean,
           nmb = 100000*cuml.qaly.disc_mean - cuml.cost.disc_std) %>%
    group_by(Strategy) %>%
    summarize(nmb_mean = mean(nmb, na.rm = TRUE), .groups = "keep")

  opt_strat_all[i] <- as.character(df_strat$Strategy[which.max(df_strat$nmb_mean)])
}
for (i in 1:length(int.cost)) {
  df_strat <- df_cov %>%
    mutate(Strategy = as.factor(paste0(ifelse(prep.optim.init == T, "I", "-"),
                                       ifelse(prep.optim.adhr == T, "A", "-"),
                                       ifelse(prep.optim.retn == T, "P", "-")))) %>%
    select(-c(prep.optim.init, prep.optim.adhr, prep.optim.retn)) %>%
  rowwise() %>%
    mutate(cuml.init.int.cost.disc_std = ifelse(cuml.init.int.cost.disc_mean == 0,
                                                0,
                                                (cuml.init.int.cost.disc_mean - fixed) * init.adj + fixed),
           int.cost.disc_mean = int.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std,
           cuml.cost.disc_mean = cuml.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std,
           cuml.cost.disc_std = cuml.cost.disc_mean - cuml.init.int.cost.disc_std + int.cost[i]*cuml.init.int.cost.disc_std,
           nmb = 100000*cuml.qaly.disc_mean - cuml.cost.disc_std) %>%
    group_by(Strategy) %>%
    summarize(nmb_mean = mean(nmb, na.rm = TRUE), .groups = "keep")

  opt_strat_init[i] <- as.character(df_strat$Strategy[which.max(df_strat$nmb_mean)])
}
for (i in 1:length(int.cost)) {
  df_strat <- df_cov %>%
    mutate(Strategy = as.factor(paste0(ifelse(prep.optim.init == T, "I", "-"),
                                       ifelse(prep.optim.adhr == T, "A", "-"),
                                       ifelse(prep.optim.retn == T, "P", "-")))) %>%
    select(-c(prep.optim.init, prep.optim.adhr, prep.optim.retn)) %>%
  rowwise() %>%
    mutate(cuml.init.int.cost.disc_std = ifelse(cuml.init.int.cost.disc_mean == 0,
                                                0,
                                                (cuml.init.int.cost.disc_mean - fixed) * init.adj + fixed),
           int.cost.disc_mean = int.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std,
           cuml.cost.disc_mean = cuml.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std,
           cuml.cost.disc_std = cuml.cost.disc_mean  - cuml.adhr.int.cost.disc_mean + int.cost[i]*cuml.adhr.int.cost.disc_mean,
           nmb = 100000*cuml.qaly.disc_mean - cuml.cost.disc_std) %>%
    group_by(Strategy) %>%
    summarize(nmb_mean = mean(nmb, na.rm = TRUE), .groups = "keep")

  opt_strat_adhr[i] <- as.character(df_strat$Strategy[which.max(df_strat$nmb_mean)])
}
for (i in 1:length(int.cost)) {
  df_strat <- df_cov %>%
    mutate(Strategy = as.factor(paste0(ifelse(prep.optim.init == T, "I", "-"),
                                       ifelse(prep.optim.adhr == T, "A", "-"),
                                       ifelse(prep.optim.retn == T, "P", "-")))) %>%
    select(-c(prep.optim.init, prep.optim.adhr, prep.optim.retn)) %>%
  rowwise() %>%
    mutate(cuml.init.int.cost.disc_std = ifelse(cuml.init.int.cost.disc_mean == 0,
                                                0,
                                                (cuml.init.int.cost.disc_mean - fixed) * init.adj + fixed),
           int.cost.disc_mean = int.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std,
           cuml.cost.disc_mean = cuml.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std,
           cuml.cost.disc_std = cuml.cost.disc_mean - cuml.retn.int.cost.disc_mean + int.cost[i]*cuml.retn.int.cost.disc_mean,
           nmb = 100000*cuml.qaly.disc_mean - cuml.cost.disc_std) %>%
    group_by(Strategy) %>%
    summarize(nmb_mean = mean(nmb, na.rm = TRUE), .groups = "keep")

  opt_strat_retn[i] <- as.character(df_strat$Strategy[which.max(df_strat$nmb_mean)])
}

opt_df <- data.frame(int_cost = int.cost, 
                     opt_strat = c(factor(opt_strat_all, levels = levels(df_strat$Strategy)),
                                   factor(opt_strat_init, levels = levels(df_strat$Strategy)),
                                   factor(opt_strat_adhr, levels = levels(df_strat$Strategy)),
                                   factor(opt_strat_retn, levels = levels(df_strat$Strategy))),
                     param = as.factor(c(rep("all", length(int.cost)),
                               rep("init", length(int.cost)),
                               rep("adhr", length(int.cost)),
                               rep("retn", length(int.cost))))) %>%
  mutate(opt_strat = factor(df_strat$Strategy[opt_strat], levels = rev(levels(df_strat$Strategy))))

min <- opt_df %>% group_by(opt_strat, param) %>% filter(int_cost == min(int_cost)) %>% mutate(smin = int_cost) %>% select(-int_cost)
max <- opt_df %>% group_by(opt_strat, param) %>% filter(int_cost == max(int_cost)) %>% mutate(smax = int_cost) %>% select(-int_cost)
opt_plot <- left_join(min, max)
opt_plot$param <- factor(opt_plot$param, levels = c("all", "init", "adhr", "retn"), labels = c("All", "Initiation", "Adherence", "Persistence"))


g_all <- ggplot(opt_plot) +
    geom_rect(aes_(xmin = as.name("smin"), xmax = as.name("smax"),
                   ymin = 0, ymax = 1,
                   fill = as.name("opt_strat")),
              position = "identity") + xlab("Intervention Cost Scale") +
    theme(axis.line.y = element_blank(),
          axis.text.y = element_blank(),
          axis.title.y = element_blank(),
          axis.ticks.y = element_blank()) +
  labs(fill = "Optimal Strategy") +
  facet_grid(param~.)
g_all
```

LOW COVERAGE
15% start adherence intervention
20% start retention intervention
12.5% of undiagnosed MSM are using initiation app

```{r}
fixed <- sum((1 - 0.03) ^ (1:(52*10) / 52) * (1659.54*12 / 52))
init.adj <- 172.33 / 93.28

df_cov <- df[1:8,]
  df_strat <- df_cov %>%
    mutate(Strategy = as.factor(paste0(ifelse(prep.optim.init == T, "I", "-"),
                                       ifelse(prep.optim.adhr == T, "A", "-"),
                                       ifelse(prep.optim.retn == T, "P", "-")))) %>%
    select(-c(prep.optim.init, prep.optim.adhr, prep.optim.retn)) %>%
    rowwise() %>%
    mutate(cuml.init.int.cost.disc_std = ifelse(cuml.init.int.cost.disc_mean == 0,
                                                0,
                                                (cuml.init.int.cost.disc_mean - fixed) * init.adj + fixed),
           cuml.cost.disc_mean = cuml.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std,
           int.cost.disc_mean = int.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std)

  plotdat <- df_strat %>% select(Strategy, incid_mean, int.cost.disc_mean,
                                 cuml.cost.disc_mean, cuml.qaly.disc_mean)

  icer_df <- data.frame(Strategy = unique(df_strat$Strategy))
  icer_df$cost <- 10*df_strat$cuml.cost.disc_mean
  icer_df$qaly <- 10*df_strat$cuml.qaly.disc_mean

  icers <- calculate_icers(cost = icer_df$cost,
                           effect = icer_df$qaly,
                           strategies = icer_df$Strategy)
  plot(icers, label = "all")

  extra_outcomes <- plotdat %>%
    group_by(Strategy) %>%
    summarize(intervention_cost = 10*mean(int.cost.disc_mean),
              cuml_incidence = 10*mean(incid_mean),
              .groups = "keep") %>%
    ungroup() %>%
    mutate(infections_averted = 10*(first(cuml_incidence) - cuml_incidence),
           pct_infections_averted = 100*(infections_averted / (10*first(cuml_incidence))))

  icers_exp <- left_join(icers, extra_outcomes, by = "Strategy")

  sq <- icers_exp %>% filter(Strategy == "---")

  icers_exp <- icers_exp %>%
    mutate(pct_intervention_cost = 100 * (intervention_cost / Cost),
           Cost_sq_diff = Cost - sq$Cost,
           Effect_sq_diff = Effect - sq$Effect)
  icers_exp %>% 
  select(-c("cuml_incidence", "pct_intervention_cost")) %>%
  kable() %>%
  kable_styling()

```



HIGH COVERAGE
60% start adherence intervention
80% start retention intervention
30.5% of undiagnosed MSM are using initiation app

```{r}
fixed <- sum((1 - 0.03) ^ (1:(52*10) / 52) * (1659.54*12 / 52))
init.adj <- 172.33 / 93.28

df_cov <- df[17:24,]
  df_strat <- df_cov %>%
    mutate(Strategy = as.factor(paste0(ifelse(prep.optim.init == T, "I", "-"),
                                       ifelse(prep.optim.adhr == T, "A", "-"),
                                       ifelse(prep.optim.retn == T, "P", "-")))) %>%
    select(-c(prep.optim.init, prep.optim.adhr, prep.optim.retn)) %>%
    rowwise() %>%
    mutate(cuml.init.int.cost.disc_std = ifelse(cuml.init.int.cost.disc_mean == 0,
                                                0,
                                                (cuml.init.int.cost.disc_mean - fixed) * init.adj + fixed),
           cuml.cost.disc_mean = cuml.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std,
           int.cost.disc_mean = int.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std)

    plotdat <- df_strat %>% select(Strategy, incid_mean, int.cost.disc_mean,
                                 cuml.cost.disc_mean, cuml.qaly.disc_mean)

  icer_df <- data.frame(Strategy = unique(df_strat$Strategy))
  icer_df$cost <- 10*df_strat$cuml.cost.disc_mean
  icer_df$qaly <- 10*df_strat$cuml.qaly.disc_mean

  icers <- calculate_icers(cost = icer_df$cost,
                           effect = icer_df$qaly,
                           strategies = icer_df$Strategy)
  # icers
  plot(icers, label = "all")

  extra_outcomes <- plotdat %>%
    group_by(Strategy) %>%
    summarize(intervention_cost = 10*mean(int.cost.disc_mean),
              cuml_incidence = 10*mean(incid_mean),
              .groups = "keep") %>%
    ungroup() %>%
    mutate(infections_averted = 10*(first(cuml_incidence) - cuml_incidence),
           pct_infections_averted = 100*(infections_averted / (10*first(cuml_incidence))))

  icers_exp <- left_join(icers, extra_outcomes, by = "Strategy")

  sq <- icers_exp %>% filter(Strategy == "---")

  icers_exp <- icers_exp %>%
    mutate(pct_intervention_cost = 100 * (intervention_cost / Cost),
           Cost_sq_diff = Cost - sq$Cost,
           Effect_sq_diff = Effect - sq$Effect)
  icers_exp %>% 
  select(-c("cuml_incidence", "pct_intervention_cost")) %>%
  kable() %>%
  kable_styling()
```
