---
title: "10ksim_payerperspective"
author: "Greg Knowlton"
date: "3/14/2021"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.width = 12,
  fig.height = 8,
  fig.align = "center"
)
library(kableExtra)
library(dplyr)
# library(tidyverse)
library(dampack)
library(tidyr)
df <- readRDS("data/basecase_output_cleaned.rds")
```

prepCov is PrEP coverage (prevalent/eligible population)
init cov is the coverage of the initiation app (prevalent app users/eligible population)

```{r}
df[1, ] <- df[16, ]
df[17, ] <- df[16, ]
```

LOW COVERAGE
15% start adherence intervention
20% start retention intervention
12.5% of undiagnosed MSM are using initiation app

```{r}
fixed <- sum((1 - 0.03) ^ (1:(52*10) / 52) * (1659.54*12 / 52))
init.adj <- 172.33 / 93.28

df_cov <- df[1:8,]
  df_strat <- df_cov %>%
    mutate(Strategy = as.factor(paste0(ifelse(prep.optim.init == T, "I", "-"),
                                       ifelse(prep.optim.adhr == T, "A", "-"),
                                       ifelse(prep.optim.retn == T, "P", "-")))) %>%
    select(-c(prep.optim.init, prep.optim.adhr, prep.optim.retn)) %>%
    rowwise() %>%
    mutate(cuml.init.int.cost.disc_std = ifelse(cuml.init.int.cost.disc_mean == 0,
                                                0,
                                                (cuml.init.int.cost.disc_mean - fixed) * init.adj + fixed),
           cuml.cost.disc_mean = int.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std,
           int.cost.disc_mean = int.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std)

  plotdat <- df_strat %>% select(Strategy, incid_mean, int.cost.disc_mean,
                                 cuml.cost.disc_mean, cuml.qaly.disc_mean)

  icer_df <- data.frame(Strategy = unique(df_strat$Strategy))
  icer_df$cost <- 10*df_strat$cuml.cost.disc_mean
  icer_df$qaly <- 10*df_strat$cuml.qaly.disc_mean

  icers <- calculate_icers(cost = icer_df$cost,
                           effect = icer_df$qaly,
                           strategies = icer_df$Strategy)
  # icers
  plot(icers, label = "all")

  icers %>% 
  kable() %>%
  kable_styling()

```

BASE CASE COVERAGE
30% start adherence intervention
40% start retention intervention
22.5% of undiagnosed MSM are using initiation app

```{r}
fixed <- sum((1 - 0.03) ^ (1:(52*10) / 52) * (1659.54*12 / 52))
init.adj <- 172.33 / 93.28

df_cov <- df[9:16,]
  df_strat <- df_cov %>%
    mutate(Strategy = as.factor(paste0(ifelse(prep.optim.init == T, "I", "-"),
                                       ifelse(prep.optim.adhr == T, "A", "-"),
                                       ifelse(prep.optim.retn == T, "P", "-")))) %>%
    select(-c(prep.optim.init, prep.optim.adhr, prep.optim.retn)) %>%
    rowwise() %>%
    mutate(cuml.init.int.cost.disc_std = ifelse(cuml.init.int.cost.disc_mean == 0,
                                                0,
                                                (cuml.init.int.cost.disc_mean - fixed) * init.adj + fixed),
           cuml.cost.disc_mean = int.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std,
           int.cost.disc_mean = int.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std)

  plotdat <- df_strat %>% select(Strategy, incid_mean, int.cost.disc_mean,
                                 cuml.cost.disc_mean, cuml.qaly.disc_mean)

  icer_df <- data.frame(Strategy = unique(df_strat$Strategy))
  icer_df$cost <- 10*df_strat$cuml.cost.disc_mean
  icer_df$qaly <- 10*df_strat$cuml.qaly.disc_mean

  icers <- calculate_icers(cost = icer_df$cost,
                           effect = icer_df$qaly,
                           strategies = icer_df$Strategy)
  # icers
  plot(icers, label = "all")

  
  icers %>% 
  kable() %>%
  kable_styling()

```

HIGH COVERAGE
60% start adherence intervention
80% start retention intervention
30.5% of undiagnosed MSM are using initiation app

```{r}
fixed <- sum((1 - 0.03) ^ (1:(52*10) / 52) * (1659.54*12 / 52))
init.adj <- 172.33 / 93.28

df_cov <- df[17:24,]
  df_strat <- df_cov %>%
    mutate(Strategy = as.factor(paste0(ifelse(prep.optim.init == T, "I", "-"),
                                       ifelse(prep.optim.adhr == T, "A", "-"),
                                       ifelse(prep.optim.retn == T, "P", "-")))) %>%
    select(-c(prep.optim.init, prep.optim.adhr, prep.optim.retn)) %>%
    rowwise() %>%
    mutate(cuml.init.int.cost.disc_std = ifelse(cuml.init.int.cost.disc_mean == 0,
                                                0,
                                                (cuml.init.int.cost.disc_mean - fixed) * init.adj + fixed),
           cuml.cost.disc_mean = int.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std,
           int.cost.disc_mean = int.cost.disc_mean - cuml.init.int.cost.disc_mean + cuml.init.int.cost.disc_std)

    plotdat <- df_strat %>% select(Strategy, incid_mean, int.cost.disc_mean,
                                 cuml.cost.disc_mean, cuml.qaly.disc_mean)

  icer_df <- data.frame(Strategy = unique(df_strat$Strategy))
  icer_df$cost <- 10*df_strat$cuml.cost.disc_mean
  icer_df$qaly <- 10*df_strat$cuml.qaly.disc_mean

  icers <- calculate_icers(cost = icer_df$cost,
                           effect = icer_df$qaly,
                           strategies = icer_df$Strategy)
  # icers
  plot(icers, label = "all")

  icers %>% 
  kable() %>%
  kable_styling()
```

